Query Optimization for Dynamic Imputation

### 2017-05-15 paper/experiments.tex
reference fixes, small changes

\textbf{Alternate Imputation Methods}\quad
We also experiment with mean-value imputation and hot
deck imputation (\Cref{sec:imputation}). In our implementation of mean-value imputation,
to facilitate non-blocking operation within the iterator
model, we estimate the column mean from base table histograms. Therefore,
imputations are identical no matter where the operator is placed in the query
plan. Moreover, runtimes are essentially identical regardless of the value of
$\alpha$ because the time cost of the imputation is relatively low independent of
how many tuples need to be imputed. In hot deck imputation, runtimes are also
similar across $\alpha$, because the cost of buffering
tuples and sampling at random is negligible compared to the rest of query
execution. \todo{be quantitative: In terms of accuracy, relative errors using hot deck are close to
zero; since the baseline, in this case, is hot deck imputation on the base
table, only skew in the distributions arising from filters and joins would lead
to larger errors. In some cases, skew does arise, and errors are on the same
magnitude as in the decision trees case. Indeed, \ProjectName{} yields larger
benefit when using relatively sophisticated, higher quality imputation
algorithms as opposed to simpler strategies that would even be quick to
implement on the base table.
}

>>>>

\textbf{Alternate Imputation Methods}\quad
We also experiment with mean-value imputation and hot deck imputation
(\Cref{sec:imputation}). In our implementation of mean-value imputation, to facilitate
non-blocking operation within the iterator model, we estimate the column mean from base
table histograms. Therefore, imputed values are identical no matter where the operator is
placed in the query plan (relative errors are $0$). Runtimes are in the range of
\runtimemeanlow{} to \runtimemeanhigh{} for queries using \ProjectName{}, as compared to
\runtimemeanlowbase{} to \runtimemeanhighbase{} when imputing on the base table.  Here, the
time cost of the imputation is relatively low no matter how many tuples need to be imputed.

In hot deck imputation, runtimes are also similar across $\alpha$, ranging from
\runtimehotdecklow{} to \runtimehotdeckhigh{} using dynamic imputation, as compared to
\runtimehotdecklowbase{} to \runtimehotdeckhighbase{} when imputing on the base table. In
this case, the cost of buffering tuples and sampling at random is negligible compared to the
rest of query execution. Relative errors using hot deck are close to zero, ranging from
\smapehotdecklow{}--\smapehotdeckhigh{}\%. (The exception is \Cref{q8} with $\alpha=1$, which has error
of \smapehotdeckhighoutlier{}\% and exhibits significant skew.) Since the baseline, in these
cases, is hot deck imputation on the base table, it is skew in the distributions arising from
filters and joins that often leads to larger errors. Indeed, \ProjectName{} yields
larger benefit when using relatively sophisticated, higher quality imputation algorithms as
opposed to simpler strategies that would even be quick to implement on the base table.
